\documentclass{mypresentation}

\begin{document}

\firstpage{Becoming a Better Programmer}{Pete Goodliffe}


\section{Author}
\begin{itemize}
\item Pete Goodliffe
\item programmer (OS implementation, audio codecs, multimedia applications, embedded firmware...)
\item software development columnist
\item also wrote
	\begin{itemize}
	\item \textit{Code Craft: The Practice of Writing Excellent Code} (No Starch Press)
	\item \textit{97 Things Every Programmer Should Know} (O'Reilly)
	\end{itemize}
\end{itemize}
\newpage


\section{Presentation}
Goodliffe presents advices that he’s learned in 15 years of professional programming.
\begin{itemize}
\item Code techniques 
\item Practices, approaches, and attitudes
\item Tactics for learning effectively, behaving ethically, finding challenges, and avoiding stagnation
\item Practical ways to complete things
\item Habits for working well with others
\end{itemize}
\newpage


\section{Table of contents}
\begin{enumerate}
\item you.write(code);
\item Practice Makes Perfect (techniques, practices, approaches to writing good code)
\item Getting Personal (skills and attitudes)
\item Getting Things Done (organisation)
\item The People Pursuit (social, work with others)
\end{enumerate}

\bigskip
Each chapter ends with a list of questions: how do you do it?
\newpage


\section{you.write(code);}
Navigating a route - how can a new team member be productive?
\begin{itemize}
\item talk to someone who knows the code
\item easy checkout and run
\item trust code, not documentation
\item modify code to learn it
\item ...
\end{itemize}
\newpage


Questions:
\begin{itemize}
\item What are the common tools you use to investigate a project?
\item Describe some strategies for adding new code to a system you don't understand fully yet.
\item How can you make code easier for a new recruit to understand? 
\item What should you do now to improve the state of your current project?
\item ...
\end{itemize}
\newpage


other topics:
\begin{itemize}
\item Care about the code
\item Write Less Code!
\item Improve Code by Refactoring
\item Don't Ignore That Error!
\item Testing Times
\item Coping with Complexity
\item ...
\end{itemize}
\newpage


\section{Practice Makes Perfect}
Nothing Is Set in Stone
\begin{itemize}
\item If you have “unchangeable” code in your product, then your product will rot.
\item Do not let the code, or the processes around it, dictate how the code grows.
\item To modify code you need courage and skill. Not recklessness.
\item Attitude: “Good code” is not somebody else’s problem. It is your respon‐ sibility.
\item ...
\end{itemize}
\newpage

Questions:
\begin{itemize}
\item What particular attributes make software easy to change? Do you naturally write software like this? 
\item How can we balance “no code ownership” with the fact that some people have more experience than others?
\item Every project has code that changes little. How much of rigid code do you have?
\item Does your project tooling support your code changes?
\item ...
\end{itemize}
\newpage

Other topics:
\begin{itemize}
\item Keep It Simple
\item Use Your Brain
\item A Case for Code Reuse
\item Effective Version Control
\item Please Release me
\item ...
\end{itemize}
\newpage

\section{Getting Personal}
Avoid Stagnation
\begin{itemize}
\item Be wary of stagnation. Seeking to become a better programmer, by definition, is not the most comfortable lifestyle.
\item Expect to invest time and effort to grow your skill set. This is a worthwhile investment; it will repay itself.
\item Stop using the same tools, languages
\item Start using a different OS
\item (Adjust your diet or go to bed earlier !)
\item ...
\end{itemize}
\newpage

Questions:
\begin{itemize}
\item Are you currently stagnating? 
\item What was the last new thing you learnt?
\item What new skill should you learn next? How will you learn it? What books, courses, or online material will you use?
\item Are you in the right job at the moment? Do you enjoy it, or has all the joy been sucked out? Are you working the 9-to-5, or are you enthused and engaged to see your project succeed? Should you look around for new challenges?
\item ...
\end{itemize}
\newpage

Other topics:
\begin{itemize}
\item Live to Love to Learn
\item Test-Driven Development
\item The Ethical Programmer
\item A Love for Languages
\item ...
\end{itemize}
\newpage

\section{Getting Things Done}
It's Done When It's Done
\begin{itemize}
\item Split large tasks up into a series of smaller, well-understood tasks.
\item Make sure you define “done.”
\item If you can’t tell when it’s done, then you shouldn’t start it.
\item Use tests written in code to define when your code is complete and working.
\item Don’t do more work than necessary. Work until you’re “done.” Then stop.
\item ...
\end{itemize}
\newpage

Questions:
\begin{itemize}
\item Do you know when your current task will be “done”? What does “done” look like?
\item Have you decomposed your current task into a single goal, or a series of simple goals?
\item How does your current development process determine how you break up and estimate work? Is it sufficient?
\item ...
\end{itemize}
\newpage

Other topics:
\begin{itemize}
\item Smarter, Not Harder
\item This Time I've Got It...
\end{itemize}
\newpage

\section{The People Pursuit}
Speak Up! Communication through code and interpersonal communication
\begin{itemize}
\item Take care to use the right vocabulary with the right people.
\item Effective communication requires focus.
\item Good communication fosters good code. The shape of your communications will shape your code.
\item Speak to others transparently, with a healthy attitude, to foster effective teamwork.
\item ...
\end{itemize}
\newpage

Questions:
\begin{itemize}
\item How does personality type affect your communication skills?
\item How does communication with a manager differ from communication with a fellow coder?
\item How do you best communicate a code design? They say a picture speaks a thousand words. Is this true?
\item Do distributed teams need to interact and communicate more than colocated teams?
\item What are the most common barriers to effective communication?
\item ...
\end{itemize}
\newpage

Other topics:
\begin{itemize}
\item People power
\item Many-festos
\item And Ode to Code
\end{itemize}
\newpage

\section{Review}
\begin{itemize}
\item a lot of good advices
\item very concrete topics that can be easily reflected on our projects
\item not only technical (technical part is the less interesting one!)
\item concrete advice at the end of each chapter: \textit{"Over the next week, keep a watch on all the ways you communicate with other people. Determine two practical things you could do to improve the quality of your communications."}
\item it's not a book you read and throw away. It's for continuous reading.
\item very challenging!
\end{itemize}
\newpage

\lastpage{That's it!}{}

\end{document}
